\documentclass[12pt]{report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{color}
\graphicspath{{images/}}
\usepackage{subcaption}
\usepackage{titlesec}
\usepackage[square, authoryear, comma, sort&compress,numbers]{natbib}
\usepackage{todonotes}
\setcounter{secnumdepth}{4}
% Biblography
\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{apalike}
% Makes subsubsub section
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}


\begin{document}


\section{Introduction}


\subsection{Background and Motivation}
Transitioning from non-renewable energy sources to renewable energy sources is one of the largest, if not the larges political challenge of today. Renewable energy is less polluting that non-renewable energy and should therefore be preferred. However, renewable energy sources make up only 17.05 percent of the worlds energy sources as of 26th of May 2015 (renewableenergyworld.com). \\

\noindent Wind turbine technology is a promising source of renewable energy. Wind turbine technology advances has led to wind turbines able to produce more energy to lower costs. However, wind turbines still produces less energy than predicted because of wake effect. For wind energy to become a larger part of the worlds energy sources sofisticated methods for wind turbine placement in wind farms needs to be developed so that each turbine produce as much energy as possible. 


\subsection{Goal and Research Questions}
This section states the goal statement and research questions that will be investigated in this thesis. \\


\noindent \textbf{Goal statement}


\begin{quote}
\textit{The project goal is to investigate the advantages of using distributed genetic algorithms to optimizing wind farm layout, i.e. solving the wind farm layout optimization problem.}
\end{quote}


\noindent The performance of distributed genetic algorithms will be studied and compared to the performance of a simple genetic algorithm (not distributed) as well as to each other, with the goal of answering the research questions stated below.\\


\noindent \textbf{Research question 1}


\begin{quote}
\textit{Can distributed genetic algorithms improve the quality of the solution to the wind farm layout optimization problem as compared to simple genetic algorithm.}
\end{quote}


\noindent \textbf{Research question 2}


\begin{quote}
\textit{Which distributed genetic algorithm works best for the wind farm layout optimization problem? What properties are essential for its success?}
\end{quote}



\end{document}